cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added Mobius

@@

>>>>

The `gen_mobius(n, p)` function generates a dataset of $n$ points that form a Mobius strip embedded in the first three dimensions of a $p$-dimensional space. This classical non-orientable surface loops back on itself with a half-twist.

The Mobius strip is generated using `geozoo::mobius(n, p = 3)$points`, which samples $n$ points from a parametrization of the surface defined by angle $\theta$ and strip width $w$. The cartesian coordinates are;

$$
X\_1 = \left(1 + \frac{w}{2} \cos(\theta/2)\right) \cos(\theta),
$$
$$
X\_2 = \left(1 + \frac{w}{2} \cos(\theta/2)\right) \sin(\theta),
$$
$$
X\_3 = \frac{w}{2} \sin(\theta/2).
$$

This maps a $2\text{-}D$ band with a half-twist into $3\text{-}D$ space, forming a non-orientable 1-sided surface.

For $p > 3$, the function appends $p - 3$ dimensions with small Gaussian noise:

$$
x_j \sim \mathcal{N}(0, 0.05^2), \quad j = 4, \dots, p.
$$

@@

- Mobius: The core geometric structure is a Mobius strip—a classic one-sided surface with a half-twist—useful for evaluating how well methods capture non-orientability and twisted manifolds.
